AmphibBio

### 2019-08-07 data-raw/amphibio.Rmd
Handle multiple trait database matches to the same ITIS id.

>>>>

Check for multiple matches to the same ID
```{r}
#get ids that have more than one entry
dupe_ids <- amphibio %>% 
  select(id, sourceName) %>% 
  drop_na(id) %>%
  distinct() %>% 
  group_by(id) %>% 
  filter(n() > 1) %>%
  pull(id)

#get data associated with ids
dupe_data <- amphibio %>% 
  filter(id %in% dupe_ids)

#resolve so that traits are averaged for species that need to be combined
resolved <- dupe_data %>%
  select(-scientificName, -sourceName) %>%
  group_by(id) %>%
  summarise_all(~ if (all(is.na(.))) {NA} else {mean(., na.rm = TRUE)}) %>%
  mutate(scientificName = get_names(id))

#remove unresolved data and replace with new resolved
amphibio <-  amphibio %>% 
  anti_join(dupe_data) %>% 
  bind_rows(resolved)

```
